Evolution Reinforces Cooperation with the Emergence of Self-Recognition Mechanisms: an Empirical Study of the Moran process for the Iterated Prisoner's Dilemma

### 2017-11-01 main.tex
Revert "Correct detail about repetitions of Moran process."
This reverts commit 641b44bb106766472f7d2cd9f426040a0886879a.

The Moran process is run for each strategy pair to fixation
with starting population distributions of $(1, N-1)$, $(N/2, N/2)$ and $(N-1 ,
1)$, for \(N\) from 2 through 14. The fixation probability is then empirically
computed for each combination of starting distribution and value of \(N\).  The
Axelrod library can carry out exact simulations of the Moran process. Since some
of the strategies have a high computational cost or are stochastic, samples are
taken from a large number of 200 turn match outcomes for the pairs of players
for use in computing fitnesses in the Moran process (i.e. a stochastic cache of
matches is used). This approach was verified to agree with unsampled
calculations to a high degree of accuracy in specific cases.  This is described
in Algorithms~\ref{alg:data_collection} and~\ref{alg:moran_process}.

>>>>

Each strategy pair is run for 1000 repetitions of the Moran process to fixation
with starting population distributions of $(1, N-1)$, $(N/2, N/2)$ and $(N-1 ,
1)$, for \(N\) from 2 through 14. The fixation probability is then empirically
computed for each combination of starting distribution and value of \(N\).  The
Axelrod library can carry out exact simulations of the Moran process. Since some
of the strategies have a high computational cost or are stochastic, samples are
taken from a large number of 200 turn match outcomes for the pairs of players
for use in computing fitnesses in the Moran process (i.e. a stochastic cache of
matches is used). This approach was verified to agree with unsampled
calculations to a high degree of accuracy in specific cases.  This is described
in Algorithms~\ref{alg:data_collection} and~\ref{alg:moran_process}.
